%-------------------------
% Resume in Latex
% Author : Jason Grant
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%\(\)


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jason Grant} \\ \vspace{1pt}
    \small (086) 072 0001 $|$ \href{mailto:jason.grant@umail.ucc.ie}
    {\underline{jason.grant@umail.ucc.ie}} $|$ 
    \href{https://linkedin.com/in/jason-grant/}{\underline{linkedin.com/in/jason-grant/}} $|$
    \href{https://github.com/jgrantprog1993}{\underline{github.com/jgrantprog1993}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {South East Technological University, Waterford Ireland}{\textbf{First Class Honours (1.1)}}
      {HDip in Computer Science}{Jan. 2021 -- May 2023}
    \resumeSubheading
      {University College Cork, Ireland}{Second Class Honours Grade 1 (2.1)}
      {Bachelor of Electrical and Electronic Engineering (BEEE) Honours Degree}{Sept. 2012 -- May 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {WEB Developer}{Nov 2022 -- Present}
      {DMI | Digital Marketing Institute}{Dublin (Remote)}
      \resumeItemListStart
        \resumeItem{Feature Development: Developed  and deployment of multiple high-impact features on the company website, using JavaScript, PHP/Laravel, SQL queries, and ExpressionEngine, improving user experience and functionality for over 50,000 users.}
        \resumeItem{API Integration: Spearheaded the seamless integration of a third-party exam provider’s API by working with OpenAPI documentation and utilizing Postman for testing, reducing manual exam management processes by 25.}
        \resumeItem{Customer Support: Balanced time between full-stack development and providing technical support to the Operations team, streamlining both internal tools and external web application updates, resulting in a 15 reduction in support tickets.}
        \resumeItem{Proof of Concept (POC) Development: Designed and built a learner exam experience prototype from scratch, using OpenAPI documentation, Postman, and PHP. Delivered the POC to key stakeholders, receiving approval for full-scale implementation within six months.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software and Systems Engineer}{Sep. 2020 -- Oct 2022}
      {WEST Pharma}{Waterford, Ireland}
      \resumeItemListStart
        \resumeItem{Software Integration Engineer within the Global Elastomer Automation Team, driving large-scale R\&D initiatives to modernize and automate manufacturing processes.}
        \resumeItem{Led the transformation of standalone equipment into a fully integrated, continuous-flow manufacturing line using advanced technologies such as PLC systems (Siemens, Beckhoff, Allen Bradley), OPC Server/Client, SCADA, Local Historians, and Industrial Protocols, significantly enhancing production efficiency.}
        \resumeItem{Conducted Factory Acceptance Testing (FAT) and Site Acceptance Testing (SAT) for multiple complex manufacturing systems, including packaging, vision, and molding equipment, ensuring seamless integration and compliance with operational standards.}
        \resumeItem{Developed and implemented logic and positional upgrades for KUKA Robotics, improving accuracy and functionality, resulting in a 15\% increase in production output.}
    \resumeItemListEnd

    \resumeSubheading
      {Senior Manufacturing Engineer}{Nov 2018 -- Sept 2020}
      {Stryker}{Cork, Ireland}
      \resumeItemListStart
        \resumeItem{Lead engineer in manufacturing ramp project, which included team of 10 Manufacturing, Quality and Validation Engineers.}
        \resumeItem{Contribute to corrective and preventative actions through root cause analysis and change implementations}
        \resumeItem{Completed full validation lifecycle on 10+ pieces of manufacturing equipment and cross-qualified four product families on manufacturing machines. Including Equipment qualification, first article inspection, and technical report writing.}
        \resumeItem{Responsible for training, supervising and mentoring new engineers on the full validation life cycle of Additive Manufacturing machines and the associated products.}
        \resumeItem{Promoted to Senior Engineer within the first year of employment within the team.}
        \resumeItem{Generated a cost saving of €50,000+ in annual scrap reduction by identifying an opportunity to increase spec limits on process monitoring step.
        Change included technical report, non-conformance management, Minitab statistical analysis of production data and presenting change to senior management.}
  \resumeSubHeadingListEnd

  \resumeSubheading
      {Automation Engineer}{Aug 2017 -- Nov 2018}
      {NeoDyne}{Kilkenny, Ireland}
      \resumeItemListStart
        \resumeItem{Worked in a team of two as an Automation Engineer, role included designing, site implementation
        and commissioning of the control logic for PLC code and SCADA of a new refrigeration plant in
        Glanbia.}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Examination Platform Upgrade: Pearson to Inspera} $|$ \emph{PHP/Laravel, Postman, Tailwind}}{Dec 2023 -- Mar 2024}

          \resumeItemListStart
            \resumeItem{Tasked with the scoping of migrating from one examination platform to another. Which includes allowing students to book, update and access their exams. As well as view results post exam submission and invigilation. Developed a full development road-map/plan for the following 3 months to hit our hard switch over deadline date, the project included:}
            \resumeItem{Conducted a full review of current process i.e. workflows, data-structures, databases, stored procedures, API integration's with Pearson.}
            \resumeItem{Created system on Postman, to walk through the full process with the new API endpoints that were available on Inspera's Open API site. i.e. book, update, cancel exam, retrieve exam results.}
            \resumeItem{Created a proof-of-concept in a local environment using PHP, HTML, and Tailwind, outlining all necessary pages and communications for the student journey. }
            \resumeItem{Provided extensive training to the Operations team on the new system via video tutorials, detailed documentation, live demonstrations, and one-on-one support.}
            \resumeItem{Collaborated with a team of three to handle the complete production build, testing, and deployment.}
            \resumeItem{Managed support items and troubleshooting post-launch, ensuring a smooth transition and user satisfaction.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Exam Invigilator Dashboard} $|$ \emph{JavaScript, Tailwind, AJAX}}{Mar 2024 -- April 2024}
          
          \resumeItemListStart
            \resumeItem{Developed a robust invigilator dashboard for an online examination system, allowing invigilators to monitor and manage exam candidates efficiently.}
            \resumeItem{Integrated conditional logic to restrict access based on user roles, ensuring only authorized invigilators can access specific features.}
            \resumeItem{Implemented modals for detailed candidate review, allowing invigilators to complete read and update operations on candidate data.}
            \resumeItem{Used JavaScript to dynamically generate and toggle modal content, enhancing user interaction without page reloads.}
            \resumeItem{Implemented asynchronous form submission using JavaScript's fetch API, ensuring seamless data submission and immediate feedback without disrupting the user experience.}
            \resumeItem{Provided continuous support and troubleshooting post-launch, ensuring smooth operations and addressing any issues promptly.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Loyalty App - Progressive Web App (PWA)} $|$ \emph{Next.js, Strapi, Vercel, Tailwind}}{May 2022 -- June 2022}
          \begin{center}
                 \href{https://github.com/jgrantprog1993/project_loyaltyApp}{\underline{github.com/jgrantprog1993/loyaltyApp}} 
            \end{center}
            
          \resumeItemListStart
            \resumeItem{Implemented and deployed a fully responsive full-stack progressive web app. Completed as a ‘cap-stone’ project for the higher-diploma. Developed the spec, created an agile                   project plan. Organised the project into two-week sprints with multiple milestones throughout the project. Technologies included:}
            \resumeItem{Front-end developed in Next.js, Tailwind. Also used technologies such as toastify, chart.js, axios, leaflet.js, font-awesome, react. Deployed using Vercel.}
            \resumeItem{Back-end developed using a CMS (Strapi v4.3), deployed using Heroku.}
            \resumeItem{Allows users to register as a generic user or as a business owner.}
            \resumeItem{Digital wallet for users loyalty rewards.}
            \resumeItem{Platform to encourage and track business growth for businesses.}
            \resumeItem{Scan QRCode to gain reward from business.}
          
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{CoffeeHub - Full Stack Web Application} $|$ \emph{Svelte, Hapi, MongoDB Atlas, Netlify}}{Dec 2022 -- March 2023}
          \begin{center}
                \href{https://github.com/jgrantprog1993/CoffeeHubV2_FrontEnd}{\underline{github.com/jgrantprog1993/CoffeeHubV2}} 
            \end{center}
          \resumeItemListStart
            \resumeItem{Implemented and deployed a web application with a modern front-end technology from a design specification. Delivered in stages via several stage gates (these are viewable on Github).}
            \resumeItem{Front end developed in Svelte. Also included technologies such as svelte-spa-router, leafleft.js, svelte-frappe-charts, Bulma, Font Awesome.}
            \resumeItem{Backend developed in Hapi with a deployed mongoDB Atlas.}
            \resumeItem{Deployed – frontend using Netlify, backend using Heroku.}
            \resumeItem{API interaction with openweatherAPI.}
            \resumeItem{Images saved and read from cloudinary.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, PHP, SQL (MySQL), Kotlin} \\
     \textbf{Web Development Frameworks \& Libraries}{: Next.js, React, Node.js, Svelte, Flask, Laravel, Material-UI, Tailwind, FastAPI, Hapi} \\
     \textbf{DevOps \& Cloud Technologies}{: AWS (EC2, S3, CloudWatch, DynamoDB, Load Balancing, Auto-Scaling Policies), Vercel, Heroku, Glitch, Netlify} \\
     \textbf{Tools \& Platforms}{: Git, VS Code, PyCharm, TablePlus, Sequel Pro, Mamp PRO, Postman, Arduino, Raspberry Pi} \\
     \textbf{APIs \& Databases}{: OpenAPI, RESTful APIs, Postman, MongoDB Atlas, Cloudinary, SQL (MySQL)} \\
     \textbf{Content Management Systems (CMS)}{:Strapi CMS, ExpressionEngine} \\
     \textbf{Other Technologies}{:Leaflet.js, Metabase, MQTT, Toastify, Chart.js, Axios, Font Awesome} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
